---
title: "sigpatsearch 0.1.0"
author: "Dean Bodenham"
date: "8 August 2017"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sigpatsearch_0.1.0}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r include = FALSE}
library(sigpatsearch)
```


# Introduction

This is an introduction to the `sigpatsearch` package.

## Load the package

First, load the package:

```{r}
library(sigpatsearch)
```

## Creating objects

There are two ways to create objects:
 1. Use the method name  
 2. Use flags `use_intervals` or`use_combinations`, and `use_covariate`

### Creating a FAIS object

Here are examples for creating a FAIS object:

```{r}
sig_fais1 <- sigpatsearch(method='fais')
```

and when one tries to print the object, this is the output:


```{r}
print(sig_fais1)
```

Here are some other example for FAIS:

```{r}
sig_fais2 <- sigpatsearch(method='FAIS')
sig_fais3 <- sigpatsearch(method='FaIs')
sig_fais4 <- sigpatsearch(use_intervals=T) 
sig_fais5 <- sigpatsearch(use_intervals=T, use_covariate=F) #default use_covariate is False
sig_fais6 <- sigpatsearch(use_combinations=F)
```


### Creating a FastCMH object

Here are different ways of creating a FastCMH object:


```{r}
sig_fastcmh1 <- sigpatsearch(method='fastcmh')
sig_fastcmh2 <- sigpatsearch(method='FASTCMH')
sig_fastcmh3 <- sigpatsearch(method='FastCMH')
sig_fastcmh4 <- sigpatsearch(use_intervals=T, use_covariate=T)
sig_fastcmh5 <- sigpatsearch(use_combinations=F, use_covariate=T)
print(sig_fastcmh5)
```


### Creating a FACS object

Here are different ways of creating a FACS object:


```{r}
sig_facs1 <- sigpatsearch(method='facs')
sig_facs2 <- sigpatsearch(method='FACS')
sig_facs3 <- sigpatsearch(method='FaCs')
sig_facs4 <- sigpatsearch(use_intervals=F, use_covariate=T)
sig_facs5 <- sigpatsearch(use_intervals=F, use_covariate=F)
sig_facs6 <- sigpatsearch(use_combinations=T, use_covariate=T)
sig_facs7 <- sigpatsearch(use_combinations=T, use_covariate=F)
print(sig_facs7)
```

### Changing $\alpha$ and `lmax`

To change the significance threshold `alpha` and the maximum interval length is easy:


```{r}
sig_fais8 <- sigpatsearch(method='fais')
sig_fais8$set_alpha(0.001)
sig_fais8$set_lmax(10)
print(sig_fais8)
```

More to follow.
